---
title: "Xu-Activity-4"
author: "Haoran Xu"
date: "2024-10-3"
output:
    html_document:
      df_print: paged
---

# my-GEO712-repository

This repository is created for the GEO712 course assignment. It includes all the necessary files and scripts needed to complete the project activities.

## Project Structure

- `init.R`: Script to initialize and install required packages
- `README.Rmd`: ReadMe file for project documentation

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```



```{r}
library(here)
# install.packages("ggplot2")  # use vignette use check all items udner gg nplot2
# vignette(package = "ggplot2")
# vignette("ggplot2-specs")

# getting the pathway for working directory
getwd()
# setwd(...) 
# recommend always using the Linux/Mac style with forward slashes (/), as Windows use two backslashes (\\).

# 动态生成图片路径并保存为一个变量
image_path <- paste0(here(), "/images/renv.png")
```
/Users/horanxu/Library/CloudStorage/OneDrive-Personal/GEOG 712 - Reproducible Research Workflow with GitHub and R/Assignments/Activity 2/Haoran's first repository/images/renv.png

![renv workflow](%60r%20imag_path%60)

```{r}
renv::status()
renv::snapshot()
renv::snapshot()
renv::status()
```

# Main Research Interest

My main research interest lies in travel behavior studies which use modelling methods to understand how the outside environment, individual preferences, and societal norms may shape people's travel decisions. I want to use many different methods to discover the statistical and spatial-temporal patterns behind travel behavior. I inten to employ approaches like Bayesian logistic models or Structural Equation Modeling (SEM) to tangel the intersecting relationships between various varibales. I am also considering GeoAI technologies, such as machine learning method, as an approach to investigate into geospatial data.

# Favorites

## Favorite Music

> ps: round brackets mean album name and release year, respectively.

-   "浮躁" by 王菲 (*浮躁*, 1996)
-   "うしろ姿" by Fishmans (*宇宙 日本 世田谷*, 1998)
-   "The Predatory Wasp of the Palisades Is Out to Get Us!" by Sufjan Stevens (*Illinois*, 2004)
-   "Malamente (Cap.1: Augurio)" by Rosalía (*El mal querer*, 2018)
-   "Belinda Says" by Alvvays (*Blue Rev*, 2023)

## Favorite Equation

Global Moran's I:

$$
I = \frac{N}{W}*\frac{\sum^N_{i=1}*\sum^N_{j=1}w_{ij}(x_i-\bar{x})(x_j-\bar{x})}{\sum^N_{i=1}(x_i-\bar{x})^2}
$$\
where $N$ is the number of spatial units indexedusethis::use_github() by $i$ and $j$; $x$ is the variable of interest; $\bar{x}$ is the mean of $x$; $w_{ij}$ are the elements of a matrix of spatial weights with zeroes on the diagonal (i.e. $w_{ii}=0$); and $W$ is the sum of all $w_{ij}$ (i.e. $W=\sum^N_{i=1}{\sum^N_{j=1}{w_{ij}}}$) [1].

## Favorite Artists

| Name                | Achievements                                                                                                                                                                                                    |
|---------------------|---------------------------------------------------|
| Joni Mitchell       | Wrote and produced many records as a singer-songwriter who showcased the strengths of feminism and anti-war spirit in the 1960s and 70s.                                                                        |
| My Bloody Valentine | The British duo group created the later-defined music genre by generations of indie music lovers as "shoegazing" and their best album *loveless* is a forever legacy to the human civilization.                 |
| Arcade Fire         | Proved that indie rock can still attain commercial success through their first several acts and ultimately winning Grammy "Album of the Year" Award with their thrid full-length album *The Suburbs*.           |
| Frank Ocean         | Regarded as a music genius and released two highly-acclaimed records which became the greatest albums of the 2010s.                                                                                             |
| Cindy Lee           | As an Canadian-born drag queen artist, her latest psychedelic folk/rock record *DIAMOND JUBILEE* which was released in March 29 this year probably would probably become one the best indie records in history. |

# A Chunk of Code

```{r}
print(sum(pi^2) + (360/365))
m <- matrix(runif(1000), ncol = 10, nrow = 100)
print(m[1,])
```

[1] Wikipedia contributors. (2024, August 24). Moran's I. In *Wikipedia, The Free Encyclopedia*. Retrieved 20:20, September 19, 2024, from <https://en.wikipedia.org/w/index.php?title=Moran%27s_I&oldid=1242089215>